A Large-Scale Study of the Use of Eval in R

### 2020-08-28 inst/paper/main.tex
Add more threats

\section{Threats to Validity} The primary threat to validity is the issue of
code coverage, a cause of concern for any dynamic approach. We mitigate this by
including only those R packages in our corpus that have many reverse
dependencies and thus high code coverage. Secondly, we turn off the bytecode
compiler for this study. The bytecode compiler can also call eval. Thirdly, we
do not get source locations for \UndefinedEvalsRnd eval calls. In these cases
\eval is either passed as an argument to a higher-order functions or is defined
in a function returned by a higher-order function and the R parser does not
retain location information for \eval. However, this is a meager
\PercentUndefinedEval of all eval calls and is unlikely to affect our analysis.

>>>>

\section{Threats to Validity} The primary threat to validity is the issue of
code coverage, a cause of concern for any dynamic approach. We mitigate this by
including only those R packages in our corpus that have many reverse
dependencies and thus high code coverage. We turn off the bytecode compiler for
this study. The bytecode compiler can also call eval. We do not get source
locations for \UndefinedEvalsRnd eval calls. In these cases \eval is either
passed as an argument to a higher-order functions or is defined in a function
returned by a higher-order function and the R parser does not retain location
information for \eval. However, this is a meager \PercentUndefinedEval of all
eval calls and is unlikely to affect our analysis. We ignore calls to the native
\eval function exposed by R. We also ignore the \c{rlang::tidy_eval} function
which uses native \eval internally because \c{rlang} is used to implement a DSL
for data analysis in R. It introduces a new first-class promise object called
\c{quosure} for which it implements special evaluation support in \c{tidy_eval}.
